---
title: "Results on Data"
output: 
  html_document: 
    theme: sandstone
theme: sandstone
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Simulation study

Through synthetic data, we investigate the efficiency and the convergence of the model compared to the one implemented in *"Bayesian nonparametric change point detection for multivariate time series with missing observations"* by Danese and Corradin.

We set 1000 iteration - 500 burning

At each step we've computed the Random Index (stored in a vector) useful to evaluate the clustering performance as well as to visualize how fast the convergence to the true partition is happening. We've also compared the most common partition; gamma, theta and sigma estimate of both the model.

```{r cars}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
